\documentclass[11pt]{article}

\input{assignment-macros-2}

\setTurnIn{extra 2}
\setAuthor{Stanley Cohen (scohe001)}
\setSID{861114309}
\setHeader

\begin{document}

\begin{problems}

  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 5

  \newpage

  \problem

  \begin{theorem}[Tower of Hanoi]
      For every positive integer $N$ EVERY sequence of legal movements that moves $N$ discs from one peg to another has AT LEAST $2^N - 1$ moves.
  \end{theorem}

  \smallskip

  \begin{longFormProof}

    \step We can prove this by induction on N.  Consider the base case N=1.

    \step[S1] To move one disc to any other peg at minimum will take 1 move.
      
    \step That is, when $N = 1$, the theorem holds.

    \begin{block}[A]
      {Assume for induction that the theorem holds for moving some positive $k$ discs.}

      \step That is, moving $k$ discs takes at least $2^k - 1$ moves

      \step Call the starting post we're moving from $P_0$, call the goal post $P_1$ and the other post, $P_2$.

      \begin{block}[B]
        {Consider any legal sequence for moving $k+1$ discs from $P_0$ to $P_1$.}

        \step To accomplish this, the bottom disc (the $k+1$ disc) must make its way from $P_0$ to $P_1$.

        \step Consider the first time the $k+1$ disc is moved.

        \step By the definition of the problem, we can only move the top disc of any stack, and we cannot place it on any smaller disc.

        \step Thus to move the $k+1$ disc, the other $k$ discs cannot be on top of it or on a post it's moving to.

        \step That is, to move the $k+1$ disc, we must first stack the other $k$ discs on a post that is not $P_0$.

        \step By 4.1, moving the $k$ discs to another post will take at least $2^k-1$ moves.

        \step[S2] Moving the $k+1$ disc to any other post post will take at least $1$ move.

        \step Now consider the problem state when the $k+1$ disk is set on $P_1$.

        \step At minimum, this is the same move from step~\ref{S2}

        \step By the definition of the problem, the other $k$ discs must all be stacked on a post that is not $P_1$.

        \step Moving the $k$ discs to the target post will take at least $2^k-1$ moves.

        \step Together, this sequence will take at least $2^k-1 + 2^k-1 + 1 = 2^{k+1} - 1$ moves.

      \end{block}

      \step By block~\ref{B}, any legal sequence for moving $k+1$ discs from $P_0$ to $P_1$ will take at least $2^{k+1} - 1$.

      \step Thus, the theorem holds for $k+1$ discs.

    \end{block}

    \step By block~\ref{A} if the theorem holds for $k$ discs, then it also holds for $k+1$ discs for any positive $k$.

    \step By 3 and 5, the theorem holds.
    
  \end{longFormProof}


\end{problems}
\end{document}

%%% Local Variables:
%%% mode: latex
%%% TeX-master: t
%%% End:
